\ldots

### 2016-02-12 paper.tex
Intro

>>>>

Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text. If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
\newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
\emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word. A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association. This idea forms the basis of distributional semantics and has become mainstream in information retrieval and natural language processing tasks.

Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics. The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.
